Cartograms with Dynamic Features

### 2022-05-25 paper/section/main.tex
draft: update algorithm

\begin{algorithm}[tb!]
    \caption{Procedure to update node positions by removing overlap and prevent nodes from crossing rivers.}\label{alg:UpdateNodePosition}
    \textbf{Global variables:} \\
    $ \nodeList \gets $ a list of $ \node $ representing CCGs with the following properties: \\
    \-\hspace{1em} $ \nodeListCross \gets True $ if any $ \node $ in $ \nodeList $ crosses a river \\
    $ \nodeSize \gets $ the current size of all nodes \\
    $ \nodeSizeMax \gets $ the maximum size of a node \\
    $ \stalemateMax \gets $ the maximum number of iterations indicating a stalemate \\

@@

    \begin{algorithmic}[1]
        \Procedure{UpdateNodePosition}{}
        \While{$ \nodeSize < \nodeSizeMax $}
            \State $ \nodeListCross \gets True $
            \While{$ \nodeListCross = True $}

                \State $ \nodeListCross \gets False $
                \State $ \nodeList \gets $ RemoveOverlap ($ \nodeList $)

                \ForEach {$ \node \in \nodeList $}

@@

                        \If{ \Call{TestIntersection}{$ \nodeFNORLine $} $ = True $}
                            \State $ \nodeCross \gets \nodeCross ++ $
                            \State $ \nodeListCross \gets True $

@@

                    \State $ \nodeListCross \gets 0 $
                    \State $ \nodeList \gets $ RemoveOverlap ($ \nodeList $)
                    \color{blue}
                    \ForEach {$ \river \in \riverList $}
                        \State $ \riverVector \gets (0,0) $ \Comment{Hold the sum of vectors $ \nodeVectorCT $}
                        \ForEach {$ \node \in \nodeList $}

                            \If {$ \node(x,y) \neq \nodeFNOR(x,y) $}
                                \If{ \Call{TestIntersection}{$ \nodeFNORLine $, $ \river $} $ = True $}
                                \State $ \riverVector \gets \riverVector + \nodeVectorCT$
                                \State $ \nodeListCross \gets \nodeListCross ++ $
                                \EndIf

                        \State Translate river $ \river $ by the average vector $ \frac{\riverVector}{\nodeListCross} $
                        \State $ \nodeListCross \gets 0 $ \Comment{Clear the counter}
                    \EndFor

                    \color{black}
                    \ForEach {$ \node \in \nodeList $}

                            \If{ \Call{TestIntersection}{$ \nodeFNORLine $} $ = True $}
                                \State $ \nodeCross \gets \nodeCross ++ $
                                \State $ \nodeListCross \gets \nodeListCross++ $

>>>>

@@

                \State $ \nodeListCross \gets 0 $
                \State $ \nodeList \gets $ RemoveOverlap ($ \nodeList $)
                \color{blue}
                \State \Call{TranslateRiver}{$ \nodeList $}
                \State $\nodeListCross \gets $ \Call{TranslateNode}{$ \nodeList $}

                \color{black}

\begin{algorithm}[tb!]
    \caption{Procedure to translate rivers.}\label{alg:TranslateRiver}
    \color{blue}
    \textbf{Input:} \\
    $ \nodeList \gets $ a list of $ \node $ representing CCGs \\

    \textbf{Local variables:} \\
    $ count \gets $ the number of river crossing nodes \\
    $ \node \gets $ a node is an object with the following properties: \\
    \-\hspace{1em} $ \node.x, \node.y, $ or $ \node(x,y) \gets $ the x and y coordinates of $ \node $ \\
    \-\hspace{1em} $ \nodeCross \gets $ the counter for river crosses for $ \node $ \\
    \-\hspace{1em} $ \nodePrevious \gets $ the previous position of $ \node $ \\
    \-\hspace{1em} $ \nodeFNOR \gets $ the translated position of $ \node $ \\

    \begin{algorithmic}[1]
        \Procedure{TranslateRiver}{$ \nodeList $}
        \ForEach {$ \river \in \riverList $}
        \State $ count \gets 0 $
        \State $ \riverVector \gets (0,0) $ \Comment{Hold the sum of vectors $ \nodeVectorCT $}
        \ForEach {$ \node \in \nodeList $}

        \If {$ \node(x,y) \neq \nodeFNOR(x,y) $}
        \If{ \Call{TestIntersection}{$ \nodeFNORLine $, $ \river $} $ = True $}
        \State $ \riverVector \gets \riverVector + \nodeVectorCT$
        \State $ count \gets count ++ $
        \EndIf

        \State Translate river $ \river $ by the average vector $ \frac{\riverVector}{count} $
        \EndFor

\begin{algorithm}[tb!]
    \caption{Procedure to translate node positions.}\label{alg:TranslateNode}

    \color{blue}
    \textbf{Input:} \\
    $ \nodeList \gets $ a list of $ \node $ representing CCGs \\

    \textbf{Output:} \\
    $ count \gets $ the number of river crossing nodes in the input \\

    \textbf{Global variables:} \\
    $ \stalemateMax \gets $ the maximum number of iterations indicating a stalemate \\

    \begin{algorithmic}[1]
        \Procedure{TranslateNode}{$ \nodeList $}
        \State $ count \gets 0 $
        \ForEach {$ \node \in \nodeList $}

@@

                        \If{ \Call{TestIntersection}{$ \nodeFNORLine $} $ = True $}
                            \State $ \nodeCross \gets \nodeCross ++ $
                            \State $ count \gets count ++ $

@@

                \EndFor
        \State \Return{$ count $}
        \EndProcedure
    \end{algorithmic}
\end{algorithm}

\color{black}
